---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Project Quick Start

<!-- badges: start -->

[![R-CMD-check](https://github.com/zawmtun/nightingale/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zawmtun/nightingale/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of nightingale is to provide an exemplary R package for learning and trying out practices of research software engineering.

## The team

**Members:** Jan Simson, Fritjof Jammers

## Installation

You can install the development version of nightingale from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jansim/nightingale")
```

## Example

This is a basic example which shows you how to use the package. First load the package into the environment:

```{r load-package, eval=FALSE}
library(nightingale)
```

To create a barplot of mortality data:

```{r eval=FALSE}
show_barplot()
```

To launch a Shiny dashboard for the mortality data:

```{r eval=FALSE}
show_shiny_app()
```

## License

This package is licensed under the MIT License.\
See the LICENSE file for details.

## Contact

**Reach out:**

-   Jan Simson: [jan.simson\@lmu.de](mailto:jan.simson@lmu.de){.email}

-   Fritjof Jammers: [fritjoflammers\@gmail.com](mailto:fritjoflammers@gmail.com){.email}
